---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# svg hex

The files in this folder are the result of playing around with svg. I used the R
package [minisvg](https://github.com/coolbutuseless/minisvg/). The tree was
created with [flametree](https://github.com/djnavarro/flametree).

```{r echo=FALSE}
knitr::include_graphics("minisvg_with_tree.svg")
```

The final svg [minisvg.svg](minisvg.svg) is created with
[create_svg_hex.R](create_svg_hex.R). Unfortunately, the file is not completely
rendered when you view it on github. But when you download it, you can can view
it correctly in firefox. This is because the file includes svg child images from the
internet. Those are only correctly shown when I render it as a local file on 
my machine. 

However, I made another standalone svg file
[minisvg_with_tree.svg](minisvg_with_tree.svg) (which is shown in this readme),
where I copy-pasted the single elements of the [tree2.svg](tree2.svg) file into
the hex svg. It has some bizarre unintentional effects, but looks interesting
though.


